A Plot is Worth a Thousand Tests: Assessing Residual Diagnostics with the Lineup Protocol

### 2023-05-04 appendix.Rmd
final changes

Following the terminology introduced by @kullback1951information, $P$ represents the measured probability distribution, and $Q$ represents the assumed probability distribution. The Kullback-Leibler divergence is defined as $\int_{-\infty}^{\infty}log(p(x)/q(x))p(x)dx$, where $p(.)$ and $q(.)$ denote probability densities of $P$ and $Q$.

@@

Because $rank(\boldsymbol{R}) = n - p - 1 < n$, $\boldsymbol{e}$ follows a degenerate multivariate normal distribution and does not have a density. Since the Kullback-Leibler divergence requires a proper density function, we need to simplify the covariance matrix of $\boldsymbol{e}$ by setting all the off-diagonal elements to 0. Then, the residuals will be assumed to follow $N(\boldsymbol{0}, diag(\boldsymbol{R}\sigma^2))$ under the null hypothesis that the model is correctly specified. If the model is however misspecified due to omitted variables $\boldsymbol{Z}$, or a non-constant variance $\boldsymbol{V}$, the distribution of residuals can be derived as $N(\boldsymbol{R}\boldsymbol{Z}\boldsymbol{\beta}_z, diag(\boldsymbol{R}\sigma^2))$ and $N(\boldsymbol{0}, diag(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}'))$ respectively.

By assuming both $P$ and $Q$ are multivariate normal density functions, the Kullback-Leibler divergence can be rewritten as 
$$KL = \frac{1}{2}\left(log\frac{|\Sigma_p|}{|\Sigma_q|} - n + tr(\Sigma_p^{-1}\Sigma_q) + (\mu_p - \mu_q)'\Sigma_p^{-1}(\mu_p - \mu_q)\right).$$

@@

\begin{equation*}
\label{eq:effect-size}
KL = \frac{1}{2}\left(log\frac{|diag(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}')|}{|diag(\boldsymbol{R}\sigma^2)|} - n + tr(diag(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}')^{-1}diag(\boldsymbol{R}\sigma^2)) + \boldsymbol{\mu}_z^{T}(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}')^{-1}\boldsymbol{\mu}_z\right).
\end{equation*}

@@

$$KL = \frac{1}{2}\left(\boldsymbol{\mu}_z^{T}(diag(\boldsymbol{R}\sigma^2))^{-1}\boldsymbol{\mu}_z\right).$$

@@

$$KL = \frac{1}{2}\left(log\frac{|diag(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}')|}{|diag(\boldsymbol{R}\sigma^2)|} - n + tr(diag(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}')^{-1}diag(\boldsymbol{R}\sigma^2))\right).$$
Since we assume $\sigma = 1$ for the heteroskedasticity model, the final form of the formula is

$$KL = \frac{1}{2}\left(log\frac{|diag(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}')|}{|diag(\boldsymbol{R})|} - n + tr(diag(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}')^{-1}diag(\boldsymbol{R}))\right).$$

@@

It is found in the result that the power of a RESET test will be affected by the highest order of fitted values included in the auxiliary formula. And we suspect that the current recommendation of the highest order - four, is insufficient to test complex non-linear structures such as the "Triple-U" shape designed in this paper. Figure \ref{fig:reset} illustrates the change of power of RESET test while testing the "U" shape and the "Triple-U" shape with different highest orders. Clearly, when testing a simple shape like the "U" shape, the highest order has very little impact on the power. But for testing the "Triple-U" shape, there will be a loss of power if the recommended order is used. To avoid the loss of power, the highest order needs to be set to at least six.

@@

```{r reset, fig.cap = 'Change of power of RESET tests for different orders of fitted values included in the auxiliary formula. The left panel is the power of testing the "U" shape and the right panel is the power of testing the "Triple-U" shape. The power will not be greatly affected by the highest order in the case of testing the "U" shape. In the case of testing the "Triple-U" shape, the highest order needs to be set to at least six to avoid the loss of power.', fig.height = 4}
reset_diff_dat %>%
  bind_rows(reset_diff_dat2) %>%
  mutate(shape = factor(ifelse(shape == 1, "U", "Triple-U"), levels = c("U", "Triple-U"))) %>%
  ggplot() +
  geom_line(aes(log_effect_size, power, col = as.factor(as.integer(name))),
            size = 1) +
  theme_light() +
  labs(col = "Highest order") +
  xlab(expression(log[e] (Effect_size))) +
  scale_color_brewer(palette = "Reds") +
  facet_wrap(~shape)
```

@@

```{r poly-allocate, fig.cap = 'Factor values assigned to the first 20 participants recruited during data collection period I, with data points slightly jittered to prevent overlap. Each participant have been exposed to all one-way and two-way factor combinations.'}
vi_survey %>%
  filter(exp == 3) %>%
  filter(!attention_check) %>%
  filter(set <= 20) %>%
  mutate(shape = c("U", "S", "M", "Triple-U")[shape]) %>%
  mutate(shape = factor(shape, levels = c("U", "S", "M", "Triple-U"))) %>%
  mutate(e_sigma = factor(e_sigma)) %>%
  mutate(n = factor(n)) %>%
  ggplot() +
  geom_jitter(aes(e_sigma, shape, col = n),
             width = 0.2,
             height = 0.2,
             alpha = 0.5,
             size = 3) +
  facet_wrap(~set) +
  scale_color_brewer(palette = "Dark2") +
  theme_light() +
  ylab("Non-linearity pattern") +
  xlab(expression(sigma)) +
  labs(col = "Sample size")
```

```{r heter-allocate, fig.cap = 'Factor values assigned to the first 20 participants recruited during data collection period II, with data points slightly jittered to prevent overlap. Each participant appears to have been exposed to almost all one-way and two-way factor combinations. However, two participants, namely participant 16 and participant 18, were not presented with lineups containing a butterfly shape with $b = 4$. Additionally, participant 7 did not encounter a lineup featuring a butterfly shape with $b = 1$.'}
vi_survey %>%
  filter(exp == 4) %>%
  filter(!attention_check, !null_lineup) %>%
  filter(set <= 20) %>%
  mutate(a = c("Left-triangle", "Butterfly", "Right-triangle")[a + 2]) %>%
  mutate(a = factor(a, levels = c("Left-triangle", "Butterfly", "Right-triangle"))) %>%
  mutate(b = factor(b)) %>%
  mutate(n = factor(n)) %>%
  ggplot() +
  geom_jitter(aes(b, a, col = n),
             width = 0.2,
             height = 0.2,
             alpha = 0.5,
             size = 3) +
  facet_wrap(~set) +
  scale_color_brewer(palette = "Dark2") +
  theme_light() +
  ylab("Heteroskedasticity pattern") +
  xlab("b") +
  labs(col = "Sample size")
```

>>>>

Following the terminology introduced by @kullback1951information, $P$ represents the measured probability distribution, and $Q$ represents the assumed probability distribution. The Kullback-Leibler divergence is defined as $\int_{-\infty}^{\infty}\log(p(x)/q(x))p(x)dx$, where $p(.)$ and $q(.)$ denote probability densities of $P$ and $Q$.

@@

Because $\text{rank}(\boldsymbol{R}) = n - p - 1 < n$, $\boldsymbol{e}$ follows a degenerate multivariate normal distribution and does not have a density. Since the Kullback-Leibler divergence requires a proper density function, we need to simplify the covariance matrix of $\boldsymbol{e}$ by setting all the off-diagonal elements to 0. Then, the residuals will be assumed to follow $N(\boldsymbol{0}, diag(\boldsymbol{R}\sigma^2))$ under the null hypothesis that the model is correctly specified. If the model is however misspecified due to omitted variables $\boldsymbol{Z}$, or a non-constant variance $\boldsymbol{V}$, the distribution of residuals can be derived as $N(\boldsymbol{R}\boldsymbol{Z}\boldsymbol{\beta}_z, \text{diag}(\boldsymbol{R}\sigma^2))$ and $N(\boldsymbol{0}, \text{diag}(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}'))$ respectively.

By assuming both $P$ and $Q$ are multivariate normal density functions, the Kullback-Leibler divergence can be rewritten as 
$$KL = \frac{1}{2}\left(\log\frac{|\Sigma_p|}{|\Sigma_q|} - n + \text{tr}(\Sigma_p^{-1}\Sigma_q) + (\mu_p - \mu_q)'\Sigma_p^{-1}(\mu_p - \mu_q)\right).$$

@@

\begin{equation*}
\label{eq:effect-size}
KL = \frac{1}{2}\left(\log\frac{|\text{diag}(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}')|}{|\text{diag}(\boldsymbol{R}\sigma^2)|} - n + \text{tr}(\text{diag}(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}')^{-1}\text{diag}(\boldsymbol{R}\sigma^2)) + \boldsymbol{\mu}_z'(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}')^{-1}\boldsymbol{\mu}_z\right).
\end{equation*}

@@

$$KL = \frac{1}{2}\left(\boldsymbol{\mu}_z'(\text{diag}(\boldsymbol{R}\sigma^2))^{-1}\boldsymbol{\mu}_z\right).$$

@@

$$KL = \frac{1}{2}\left(log\frac{|\text{diag}(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}')|}{|\text{diag}(\boldsymbol{R}\sigma^2)|} - n + \text{tr}(\text{diag}(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}')^{-1}
\text{diag}(\boldsymbol{R}\sigma^2))\right).$$
Since we assume $\sigma = 1$ for the heteroskedasticity model, the final form of the formula is

$$KL = \frac{1}{2}\left(\log\frac{|\text{diag}(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}')|}{|\text{diag}(\boldsymbol{R})|} - n + \text{tr}(\text{diag}(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}')^{-1}\text{diag}(\boldsymbol{R}))\right).$$

@@

It is found in the result that the power of a RESET test will be affected by the highest order of fitted values included in the auxiliary formula. And we suspect that the current recommendation of the highest order - four, is insufficient to test complex non-linear structures such as the "triple-U" shape designed in this paper. Figure \ref{fig:reset} illustrates the change of power of RESET test while testing the "U" shape and the "triple-U" shape with different highest orders. Clearly, when testing a simple shape like the "U" shape, the highest order has very little impact on the power. But for testing the "triple-U" shape, there will be a loss of power if the recommended order is used. To avoid the loss of power, the highest order needs to be set to at least six.

@@

```{r reset, fig.cap = 'Change of power of RESET tests for different orders of fitted values included in the auxiliary formula. The left panel is the power of testing the "U" shape and the right panel is the power of testing the "triple-U" shape. The power will not be greatly affected by the highest order in the case of testing the "U" shape. In the case of testing the "triple-U" shape, the highest order needs to be set to at least six to avoid the loss of power.', fig.height = 4}
reset_diff_dat %>%
  bind_rows(reset_diff_dat2) %>%
  mutate(shape = factor(ifelse(shape == 1, "U", "triple-U"), levels = c("U", "triple-U"))) %>%
  ggplot() +
  geom_line(aes(log_effect_size, power, col = as.factor(as.integer(name))),
            size = 1) +
  theme_light() +
  labs(col = "Highest order") +
  xlab(expression(log[e] (Effect_size))) +
  scale_color_brewer(palette = "Reds") +
  facet_wrap(~shape) +
  ylab("Power")
```

@@

```{r poly-allocate, fig.cap = 'Factor values assigned to the first 20 participants recruited during data collection period I, with data points slightly jittered to prevent overlap. Each participant have been exposed to all one-way and two-way factor combinations.'}
vi_survey %>%
  filter(exp == 3) %>%
  filter(!attention_check) %>%
  filter(set <= 20) %>%
  mutate(shape = c("U", "S", "M", "triple-U")[shape]) %>%
  mutate(shape = factor(shape, levels = c("U", "S", "M", "triple-U"))) %>%
  mutate(e_sigma = factor(e_sigma)) %>%
  mutate(n = factor(n)) %>%
  ggplot() +
  geom_jitter(aes(e_sigma, shape, col = n),
             width = 0.2,
             height = 0.2,
             alpha = 0.5,
             size = 3) +
  facet_wrap(~set) +
  scale_color_brewer(palette = "Dark2") +
  theme_light() +
  ylab("Non-linearity pattern") +
  xlab(expression(sigma)) +
  labs(col = "Sample size")
```

```{r heter-allocate, fig.cap = 'Factor values assigned to the first 20 participants recruited during data collection period II, with data points slightly jittered to prevent overlap. Each participant appears to have been exposed to almost all one-way and two-way factor combinations. However, two participants, namely participant 16 and participant 18, were not presented with lineups containing a butterfly shape with $b = 4$. Additionally, participant 7 did not encounter a lineup featuring a butterfly shape with $b = 1$.'}
vi_survey %>%
  filter(exp == 4) %>%
  filter(!attention_check, !null_lineup) %>%
  filter(set <= 20) %>%
  mutate(a = c("left-triangle", "butterfly", "right-triangle")[a + 2]) %>%
  mutate(a = factor(a, levels = c("left-triangle", "butterfly", "right-triangle"))) %>%
  mutate(b = factor(b)) %>%
  mutate(n = factor(n)) %>%
  ggplot() +
  geom_jitter(aes(b, a, col = n),
             width = 0.2,
             height = 0.2,
             alpha = 0.5,
             size = 3) +
  facet_wrap(~set) +
  scale_color_brewer(palette = "Dark2") +
  theme_light() +
  ylab("Heteroskedasticity pattern") +
  xlab("b") +
  labs(col = "Sample size")
```

### 2023-05-04 appendix.tex
final changes

Following the terminology introduced by \citet{kullback1951information},
\(P\) represents the measured probability distribution, and \(Q\)
represents the assumed probability distribution. The Kullback-Leibler
divergence is defined as
\(\int_{-\infty}^{\infty}log(p(x)/q(x))p(x)dx\), where \(p(.)\) and
\(q(.)\) denote probability densities of \(P\) and \(Q\).

@@

Because \(rank(\boldsymbol{R}) = n - p - 1 < n\), \(\boldsymbol{e}\)
follows a degenerate multivariate normal distribution and does not have
a density. Since the Kullback-Leibler divergence requires a proper
density function, we need to simplify the covariance matrix of
\(\boldsymbol{e}\) by setting all the off-diagonal elements to 0. Then,
the residuals will be assumed to follow
\(N(\boldsymbol{0}, diag(\boldsymbol{R}\sigma^2))\) under the null
hypothesis that the model is correctly specified. If the model is
however misspecified due to omitted variables \(\boldsymbol{Z}\), or a
non-constant variance \(\boldsymbol{V}\), the distribution of residuals
can be derived as
\(N(\boldsymbol{R}\boldsymbol{Z}\boldsymbol{\beta}_z, diag(\boldsymbol{R}\sigma^2))\)
and
\(N(\boldsymbol{0}, diag(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}'))\)
respectively.

By assuming both \(P\) and \(Q\) are multivariate normal density
functions, the Kullback-Leibler divergence can be rewritten as
\[KL = \frac{1}{2}\left(log\frac{|\Sigma_p|}{|\Sigma_q|} - n + tr(\Sigma_p^{-1}\Sigma_q) + (\mu_p - \mu_q)'\Sigma_p^{-1}(\mu_p - \mu_q)\right).\]

@@

\[KL = \frac{1}{2}\left(\boldsymbol{\mu}_z^{T}(diag(\boldsymbol{R}\sigma^2))^{-1}\boldsymbol{\mu}_z\right).\]

@@

\[KL = \frac{1}{2}\left(log\frac{|diag(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}')|}{|diag(\boldsymbol{R}\sigma^2)|} - n + tr(diag(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}')^{-1}diag(\boldsymbol{R}\sigma^2))\right).\]
Since we assume \(\sigma = 1\) for the heteroskedasticity model, the
final form of the formula is

\[KL = \frac{1}{2}\left(log\frac{|diag(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}')|}{|diag(\boldsymbol{R})|} - n + tr(diag(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}')^{-1}diag(\boldsymbol{R}))\right).\]

@@

It is found in the result that the power of a RESET test will be
affected by the highest order of fitted values included in the auxiliary
formula. And we suspect that the current recommendation of the highest
order - four, is insufficient to test complex non-linear structures such
as the ``Triple-U'' shape designed in this paper. Figure \ref{fig:reset}
illustrates the change of power of RESET test while testing the ``U''
shape and the ``Triple-U'' shape with different highest orders. Clearly,
when testing a simple shape like the ``U'' shape, the highest order has
very little impact on the power. But for testing the ``Triple-U'' shape,
there will be a loss of power if the recommended order is used. To avoid
the loss of power, the highest order needs to be set to at least six.

@@

\caption{Change of power of RESET tests for different orders of fitted values included in the auxiliary formula. The left panel is the power of testing the "U" shape and the right panel is the power of testing the "Triple-U" shape. The power will not be greatly affected by the highest order in the case of testing the "U" shape. In the case of testing the "Triple-U" shape, the highest order needs to be set to at least six to avoid the loss of power.}\label{fig:reset}
\end{figure}

@@

It would be interesting if a different conventional test significance
level results in both the visual tests and conventional tests reject
only the same residual plots, and fails to reject the same residual
plots. This would be a state where both systems agree perfectly. Figure
\ref{fig:rej-rates} examines this. Plot A shows the percentage of
residual plots rejected by the visual test, given the conventional test
rejected (solid lines) or failed to reject (dashed lines). The vertical
grey line marks significance level 0.05. When the signicance level gets
smaller, the it is possible te see that the visual tests reject (nearly)
100\% of the time that the conventional test rejects. However, there is
not agreement, because the visual tests also increasingly reject
residual plots where the conventional test failed to reject. Plot B is
comparable to an ROC curve, where the percentage visual test rejection
conditional on conventional test decision is plotted: Reject conditional
on reject is plotted against reject conditional on fail to reject, for
different significance levels. The non-linearity pattern results are
close to being ideal, that the percentage of reject relative to fail to
reject increases very slowly as the reject relative to reject converges
to 100. The heteroskedasticity pattern is more problematic, and shows
that the cost of rejecting less with the conventional test is
disagreement with the visual test.

@@

The survey data is collected via a self-hosted website designed by us.
The complete architecture is provided in Figure \ref{fig:tech}. The
website is built with the \texttt{Flask} \citep{flask} web framework and
hosted on \texttt{PythonAnywhere} \citep{pythonanywhere}. It is
configured to handle HTTP requests such that participants can correctly
receive webpages and submit responses. Embedded in the resources sent to
participants, the \texttt{jsPsych} front-end framework \citep{jspsych}
instructs participants' browsers to render an environment for running
behavioral experiments. During the experiment, this framework will
automatically collect common behavioral data such as response time and
clicks on buttons. participants' responses are first validated by a
scheduled \texttt{Python} script run on the server, then push to a
Github repository. Lineup images shown to users are saved in multiple
Github repositories and hosted in corresponding Github pages. The URLs
to these images are resolved by \texttt{Flask} and bundled in HTML
files.

>>>>

Following the terminology introduced by \citet{kullback1951information},
\(P\) represents the measured probability distribution, and \(Q\)
represents the assumed probability distribution. The Kullback-Leibler
divergence is defined as
\(\int_{-\infty}^{\infty}\log(p(x)/q(x))p(x)dx\), where \(p(.)\) and
\(q(.)\) denote probability densities of \(P\) and \(Q\).

@@

Because \(\text{rank}(\boldsymbol{R}) = n - p - 1 < n\),
\(\boldsymbol{e}\) follows a degenerate multivariate normal distribution
and does not have a density. Since the Kullback-Leibler divergence
requires a proper density function, we need to simplify the covariance
matrix of \(\boldsymbol{e}\) by setting all the off-diagonal elements to
0. Then, the residuals will be assumed to follow
\(N(\boldsymbol{0}, diag(\boldsymbol{R}\sigma^2))\) under the null
hypothesis that the model is correctly specified. If the model is
however misspecified due to omitted variables \(\boldsymbol{Z}\), or a
non-constant variance \(\boldsymbol{V}\), the distribution of residuals
can be derived as
\(N(\boldsymbol{R}\boldsymbol{Z}\boldsymbol{\beta}_z, \text{diag}(\boldsymbol{R}\sigma^2))\)
and
\(N(\boldsymbol{0}, \text{diag}(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}'))\)
respectively.

By assuming both \(P\) and \(Q\) are multivariate normal density
functions, the Kullback-Leibler divergence can be rewritten as
\[KL = \frac{1}{2}\left(\log\frac{|\Sigma_p|}{|\Sigma_q|} - n + \text{tr}(\Sigma_p^{-1}\Sigma_q) + (\mu_p - \mu_q)'\Sigma_p^{-1}(\mu_p - \mu_q)\right).\]

@@

\[KL = \frac{1}{2}\left(\boldsymbol{\mu}_z'(\text{diag}(\boldsymbol{R}\sigma^2))^{-1}\boldsymbol{\mu}_z\right).\]

@@

\[KL = \frac{1}{2}\left(log\frac{|\text{diag}(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}')|}{|\text{diag}(\boldsymbol{R}\sigma^2)|} - n + \text{tr}(\text{diag}(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}')^{-1}
\text{diag}(\boldsymbol{R}\sigma^2))\right).\] Since we assume
\(\sigma = 1\) for the heteroskedasticity model, the final form of the
formula is

\[KL = \frac{1}{2}\left(\log\frac{|\text{diag}(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}')|}{|\text{diag}(\boldsymbol{R})|} - n + \text{tr}(\text{diag}(\boldsymbol{R}\boldsymbol{V}\boldsymbol{R}')^{-1}\text{diag}(\boldsymbol{R}))\right).\]

@@

It is found in the result that the power of a RESET test will be
affected by the highest order of fitted values included in the auxiliary
formula. And we suspect that the current recommendation of the highest
order - four, is insufficient to test complex non-linear structures such
as the ``triple-U'' shape designed in this paper. Figure \ref{fig:reset}
illustrates the change of power of RESET test while testing the ``U''
shape and the ``triple-U'' shape with different highest orders. Clearly,
when testing a simple shape like the ``U'' shape, the highest order has
very little impact on the power. But for testing the ``triple-U'' shape,
there will be a loss of power if the recommended order is used. To avoid
the loss of power, the highest order needs to be set to at least six.

@@

\caption{Change of power of RESET tests for different orders of fitted values included in the auxiliary formula. The left panel is the power of testing the "U" shape and the right panel is the power of testing the "triple-U" shape. The power will not be greatly affected by the highest order in the case of testing the "U" shape. In the case of testing the "triple-U" shape, the highest order needs to be set to at least six to avoid the loss of power.}\label{fig:reset}
\end{figure}

@@

It would be interesting if a different conventional test significance
level results in both the visual tests and conventional tests reject
only the same residual plots, and fails to reject the same residual
plots. This would be a state where both systems agree perfectly. Figure
\ref{fig:rej-rates} examines this. Plot A shows the percentage of
residual plots rejected by the visual test, given the conventional test
rejected (solid lines) or failed to reject (dashed lines). The vertical
grey line marks significance level 0.05. When the significance level
gets smaller, it is possible to see that the visual tests reject
(nearly) 100\% of the time that the conventional test rejects. However,
there is no agreement, because the visual tests also increasingly reject
residual plots where the conventional test failed to reject. Plot B is
comparable to an ROC curve, where the percentage visual test rejection
conditional on conventional test decision is plotted: Reject conditional
on reject is plotted against reject conditional on fail to reject, for
different significance levels. The non-linearity pattern results are
close to being ideal, that the percentage of reject relative to fail to
reject increases very slowly as the reject relative to reject converges
to 100. The heteroskedasticity pattern is more problematic, and shows
that the cost of rejecting less with the conventional test is
disagreement with the visual test.

@@

The survey data is collected via a self-hosted website designed by us.
The complete architecture is provided in Figure \ref{fig:tech}. The
website is built with the \texttt{Flask} \citep{flask} web framework and
hosted on \texttt{PythonAnywhere} \citep{pythonanywhere}. It is
configured to handle HTTP requests such that participants can correctly
receive webpages and submit responses. Embedded in the resources sent to
participants, the \texttt{jsPsych} front-end framework \citep{jspsych}
instructs participants' browsers to render an environment for running
behavioural experiments. During the experiment, this framework will
automatically collect common behavioural data such as response time and
clicks on buttons. participants' responses are first validated by a
scheduled \texttt{Python} script run on the server, then push to a
Github repository. Lineup images shown to users are saved in multiple
Github repositories and hosted in corresponding Github pages. The URLs
to these images are resolved by \texttt{Flask} and bundled in HTML
files.

### 2023-05-04 coverletter/coverletter.Rmd
final changes

---
from: Weihao Li
fromqualifications: B.Comm (Hons)
fromtitle: PhD student
fromWWW: https://github.com/TengMCing
fromemail: patrick.li@monash.edu
fromphone: +61 3 9905 2608
fromsignature: sigfile.png
toname: Editors
toaddress: Journal of Computational and Graphical Statistics
opening: Dear Dr Jones and Dr Liang,
closing: Sincerely
spacing: 1.4
output: monash::letter
---

@@

The paper describes a problem with conventional testing for doing residual diagnostics. The work arose from preliminary research into building a computer vision model to process residual plots. When collecting the training data, from crowd-sourcing evaluations of lineups on simulated residuals, we discovered that the power of the conventional tests are much higher than the visual test. The difference was even bigger than reported in the validation of visual inference study conducted by Majumder, Hofmann and Cook (2013) in JASA, where the comparison was on regression coefficients. So we initially thought, oh this is bad for visual inference, but actually it's good for visual evaluation of residual plots and bad for conventional testing. The paper explains why this is. It should be of interest to readers, especially for analysts interested in diagnosing their models.

>>>>

---
from: Weihao Li
fromqualifications: B.Comm (Hons)
fromtitle: PhD student
fromWWW: https://github.com/TengMCing
fromemail: patrick.li@monash.edu
fromphone: +61 3 9905 2608
fromsignature: signature.png
toname: Editors
toaddress: Journal of Computational and Graphical Statistics
opening: Dear Dr Jones and Dr Liang,
closing: Sincerely
spacing: 1.4
output: monash::letter
---

@@

The paper describes a problem with conventional testing for doing residual diagnostics. The work arose from preliminary research into building a computer vision model to process residual plots. When collecting the training data, from crowd-sourcing evaluations of lineups on simulated residuals, we discovered that the power of the conventional tests are much higher than the visual test. The difference was even bigger than reported in the validation of visual inference study conducted by Majumder, Hofmann and Cook (2013) in JASA, where the comparison was on regression coefficients. While we initially thought this is bad for visual inference, on further investigation we realised this provides empirical support for the wide-spread recommendation of visual evaluation of residual plots. The paper should be of interest to readers, especially useful for model diagnostics.
